---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# boostmath

<!-- badges: start -->
[![R-CMD-check](https://github.com/andrjohns/boostmath/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/andrjohns/boostmath/actions/workflows/R-CMD-check.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/boostmath)](https://CRAN.R-project.org/package=boostmath)
[![Downloads](https://cranlogs.r-pkg.org/badges/boostmath?color=blue)](https://CRAN.R-project.org/package=boostmath)
[![boostmath status badge](https://andrjohns.r-universe.dev/badges/boostmath)](https://andrjohns.r-universe.dev/boostmath)
<!-- badges: end -->

Providing simple access to Boost's Math functions in R, no compilation required.

## Installation

You can install the development version of boostmath from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("andrjohns/boostmath")
```

Or you can install pre-built binaries from R-Universe:

```{r, eval=FALSE}
install.packages("boostmath", repos = c("https://andrjohns.r-universe.dev",
                                        "https://cran.r-project.org"))
```

## Usage

Functions can be used directly after loading the package:

```{r example}
library(boostmath)

hypergeometric_pFq(c(1, 2.5), c(0.5, 2), 1)
ibeta_inv(2.1, 5.2, 0.7)
owens_t(2.1, 4.2)
```

Any Boost Math functions that share the same name as R functions are sufffixed with `_boost` to avoid conflicts:

```{r}
beta_boost(3, 2)
lgamma_boost(5)
```

### Quadrature and Differentiation

Boost's integration and (numerical) differentiation routines are also available for use with R functions:

```{r}
trapezoidal(\(x) { 1/(5 - 4*cos(x)) }, a = 0, b = 2*pi)

gauss_legendre(\(x) { x * x * atan(x) }, a = 0, b = 1, points = 20)

gauss_kronrod(\(x) { exp(-x * x / 2) }, a = 0, b = Inf, points = 15)

tanh_sinh(\(x) { log(x)*log1p(-x) }, a = 0, b = 1)

sinh_sinh(\(x) { exp(-x*x) })

exp_sinh(\(x) { exp(-3*x) }, a = 0, b = Inf)
```
