---
title: "Boost Math: Special Functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Boost Math: Special Functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include=FALSE}
library(boostmath)
```

## Using Boost's Special Math Functions

The [Special Functions](https://www.boost.org/doc/libs/1_85_0/libs/math/doc/html/special.html) section of the Boost Math library cover a broad range of areas:

  - Number Series
  - Gamma Functions
  - Factorials and Binomial 
  - Beta Functions
  - Error Functions
  - Polynomials
  - Bessel Functions
  - Airy Functions
  - Elliptic Integrals
  - Jacobi Elliptic Functions
  - Jacobi Theta Functions
  - Lambert W function
  - Zeta Functions
  - Exponential Integrals
  - Hypergeometric Functions
  - Basic Functions
  - Sinus Cardinal and Hyperbolic Sinus Cardinal Functions
  - Inverse Hyperbolic Functions
  - Owen's T function
  
These are all exposed for direct use in `boostmath` without needing any additional compilation:

```{r}
hypergeometric_pFq(c(1, 2.5), c(0.5, 2), 1)
ibeta_inv(2.1, 5.2, 0.7)
owens_t(2.1, 4.2)
```